PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-05-25 main.tex
Start making figures look nicer
Finish editing figures
Fix broken references, update figure captions

In section \ref{sec:theory} we provide an overview of the theory behind planetesimal accretion and show that assumptions used to derive the well-known modes of growth are only valid at sufficiently long orbital periods. We then motivate the need for N-body simulations to study this problem and describe the code used, along with how our initial conditions were constructed in section \ref{sec:methods}. In section \ref{sec:results}, we present parameter study of planetesimal accretion using a series of simulations of narrow annuli at various orbital periods. We also present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods. Next, we assess the impact of simplifications made to our collision model on this result in section \ref{sec:assump}. In section \ref{sec:discuss}, we discuss the implications of this multimodal accretion behavior throughout the disk for planet formation models and conclude.

@@

In the limit that $v_{esc} \gg v$, it can be shown that $M \propto M^{4/3}$, which implies a runaway scenario, in which growth accelerates with mass. This mode of growth was confirmed with N-body simulations by \citet{kokubo96} and appears necessary to construct protoplanets within the lifetime of a protoplanetary disk. Due to the velocity dependence of the gravitational focusing effect, it isn't clear how ubiquitous this mode of growth is. In particular, encounter velocities at short orbital periods will be rather large (because $v \sim v_{k}$) and the $v_{esc} \gg v$ condition may not always be satisfied. The effect that a dynamically hot disk has on runway growth will be examined in detail in section \ref{sec:results}.

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/timescales.png}
    \caption{The ratio between the two-body relaxation and collision timescale for a population of equal-mass planetesimals. Only in regions where $t_{relax} \ll t_{coll}$ can the velocity distribution respond to changes in the mass of the bodies such that oligarchic growth can operate. This condition is no longer satisfied for a dynamically hot disk at sufficiently short orbital periods.\label{fig:timescales}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/surfden_profiles.png}
    \caption{The final state of all simulations listed in table \ref{tab:sim_properties}. Point sizes indicate the relative masses.\label{fig:surfden_profiles}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/acc_zones.png}
    \caption{For the 20 most massive bodies at the end of the fdHi simulation, the relative shape of the accretion zones for each body are shown. The black hash marks indicate the present position of the body. The accretion distributions indicate the initial locations of the planetesimals that were used to assemble a body, rather than the locations at which collisions with the massive body occurred.\label{fig:acc_zones}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/f6f4.png}
    \caption{In the top panel, we show the final masses of the bodies from the fdHi and fdHif4 simulations in units of the isolation mass for $b = 2\sqrt{3}$. The bottom panel shows the variation of $\alpha$ with orbital period for the bodies used in each case (solid curves). The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of the embryo mass distribution and isolation mass. The dotted curves in the bottom panel show the values of alpha for realistic-sized planetesimals with $\rho =$ 1, 3, 5 and 10 g cm$^{-3}$. (need to fix the green curve)\label{fig:f6f4}}
\end{center}
\end{figure}

@@

In the simulations presented in this work, all collisions result in a complete merging of a pair of bodies with no loss of mass or momentum. Although simple to model, this assumption of perfect accretion may result in overly efficient growth, particularly at the innermost region of the disk where encounter velocities are the largest. To handle this issue properly, semianalytic collision resolution models have been developed and implemented in N-body codes (see \citep{leinhardt12}). However, resolving collisional debris fragments using a direct approach as we have done with {\sc ChaNGa} would result in an intractably large number of particles.

>>>>

In section \ref{sec:theory} we provide an overview of the theory behind planetesimal accretion and show that assumptions used to derive the well-known modes of growth are only valid at sufficiently long orbital periods. We then motivate the need for N-body simulations to study this problem and describe the code used, along with how our initial conditions were constructed in section \ref{sec:methods}. In section \ref{sec:narrow}, we present a parameter study of planetesimal accretion using a series of simulations of narrow annuli at various orbital periods. We also present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods. Next, we assess the impact of simplifications made to our collision model on this result in section \ref{sec:assump}. In section \ref{sec:discuss}, we discuss the implications of this multimodal accretion behavior throughout the disk for planet formation models and conclude.

@@

In the limit that $v_{esc} \gg v$, it can be shown that $M \propto M^{4/3}$, which implies a runaway scenario, in which growth accelerates with mass. This mode of growth was confirmed with N-body simulations by \citet{kokubo96} and appears necessary to construct protoplanets within the lifetime of a protoplanetary disk. Due to the velocity dependence of the gravitational focusing effect, it isn't clear how ubiquitous this mode of growth is. In particular, encounter velocities at short orbital periods will be rather large (because $v \sim v_{k}$) and the $v_{esc} \gg v$ condition may not always be satisfied. The effect that a dynamically hot disk has on runway growth will be examined in detail in section \ref{sec:narrow}.

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/timescales.png}
    \caption{The ratio between the two-body relaxation and collision timescale for a population of equal-mass planetesimals with an internal density of 3 g cm$^{-3}$. Only in regions where $t_{relax} \ll t_{coll}$ can the velocity distribution respond to changes in the mass of the bodies such that oligarchic growth can operate. This condition is no longer satisfied for a dynamically hot disk at sufficiently short orbital periods.\label{fig:timescales}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/surfden_profiles.png}
    \caption{The final state of all simulations listed in table \ref{tab:sim_properties}. Point sizes indicate mass relative to the largest body in the fdHi simulation.\label{fig:surfden_profiles}}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/acc_zones.png}
    \caption{For the 20 most massive bodies at the end of the fdHi simulation, the relative shape of the accretion zones for each body are shown. The black hash marks indicate the present position of the body. The accretion distributions indicate the initial locations of the planetesimals that were used to assemble a body, rather than the locations at which collisions with the massive body occurred.\label{fig:acc_zones}}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/f6f4.png}
    \caption{In the top panel, we show the final masses of the bodies from the fdHi and fdHif4 simulations in units of the isolation mass for $b = 2\sqrt{3}$. The bottom panel shows the variation of $\alpha$ with orbital period for the bodies used in each case (solid curves). The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of the embryo mass distribution and isolation mass. The shaded region in the bottom panel show the values of alpha for realistic-sized (f=1) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4}}
\end{center}
\end{figure}

@@

In the simulations presented in this work, all collisions result in a complete merging of a pair of bodies with no loss of mass or momentum. Although simple to model, this assumption of perfect accretion may result in overly efficient growth, particularly at the innermost region of the disk where encounter velocities are the largest. To handle this issue properly, semianalytic collision resolution models have been developed and implemented in N-body codes (see \citet{leinhardt12}). However, resolving collisional debris fragments using a direct approach as we have done with {\sc ChaNGa} would result in an intractably large number of particles.
